{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-06-04 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

        \begin{definition}[a linear feasibility problem]

@@

            The linear feasibility problem is defined as the following optimization problem: 

@@

        The KKT of a linear programming problem is an instance of a linear feasibility problem. 

@@

@@

        \subsection{Speedy evaluations}
            Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
            Its gradient, objective value, and Bregman Divergence have: 
            \begin{align*}
                \nabla f(v) &= A^TAv - A^Td, 
                \\
                f(v) &= 
                \frac{1}{2}\langle v, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2, 
                \\
                D_f(u, v) &= (1/2)\langle u - v, A^TA (u - v)\rangle
                \\
                &= (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle. 
            \end{align*}
            The value $\nabla f(v), f(v)$ when evaluated together, require minimal additional computations. 
            This fact is favorable for implementations in practice. 
            Furthermore, the difference of the function value between 2 points $v, u$ admits an interesting relation via the Bregman Divergence. 
            Observe that $\forall u, v \in \RR^n$ it has 
            \begin{align*}
                f(u) - f(v) &= \langle \nabla f(v), u - v \rangle + D_f(u, v)
                \\
                &= \langle \nabla f(v), u - v \rangle + (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle
                \\
                &= (1/2)\langle \nabla f(u) + \nabla f(v), u - v\rangle. 
            \end{align*}
            For this problem, the computation overhead for $f(u) - f(v), D_f(u, v)$ is very little if $\nabla f(u), \nabla f(v)$ is known. 
    \section{Hoffman error bound and Q-SCNVX}

>>>>

        \begin{definition}[a conic feasibility problem]

@@

            The conic feasibility problem is defined as the following optimization problem: 

@@

        The KKT of a linear programming problem is an instance of a linear feasibility problem, with $\mathcal K$ being a cross product of one of $\RR, \RR_+, \RR_-$. 
        A feasibility semidefinite program with linear constraint can is another example. 

@@

        % SUBSECTION | INVESTIGATING THE MATRIX

@@

        % SUBSECTION | SPEEDY EVALUATION
        \subsection{Speedy evaluations}
            Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
            The gradient of $f$ at $v$ is: $\nabla f(v) = A^TAv - A^Td$. 
            Once the gradient at a point is known, the objective value at $v$, and Bregman Divergence at $u, v$ can be expressed in its gradient at $u, v$ with minimum computation overhead: 
                f(v) &= 
                \frac{1}{2}\langle v, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2, 
                D_f(u, v) &= (1/2)\langle u - v, A^TA (u - v)\rangle
                &= (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle. 
            This makes evaluating $\nabla f(v), f(v)$ together just as fast as evaluating $\nabla f(v)$ alone.
            This fact is favorable for implementations in practice. 
            Furthermore, the difference of the function value between 2 points $v, u$ admits an interesting relation via the Bregman Divergence. 
            Observe that $\forall u, v \in \RR^n$ it has: 
                f(u) - f(v) &= \langle \nabla f(v), u - v \rangle + D_f(u, v)
                &= \langle \nabla f(v), u - v \rangle + (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle
                &= (1/2)\langle \nabla f(u) + \nabla f(v), u - v\rangle. 
            For this reason, the computation overhead for $f(u) - f(v), D_f(u, v)$ is very little as well if, $\nabla f(u), \nabla f(v)$ is already known.
    \section{Hoffman error bound in linear feasibility problem}
